%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.45in,right=0.5in,bottom=0.45in]{geometry} % Document margins
\usepackage{gensymb}
\usepackage{needspace}

\name{Michael Bella} % Your name
\address{Cupertino, California 95014} % Your address
\address{408~-~717~-~0367 \\ michael.j.bella@gmail.com} % Your phone number and email

\begin{document}

% Do a thing!
\hyphenpenalty=100000

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
%\pagebreak
\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Design Experience & High Precision Analog Measurement and Design, PCB Layout \\
& Verilog, I2C, SPI, JTAG, RF Matching Network \& Amplifiers Design\smallskip \\

Lab Skills & Experienced with Oscilloscopes, Network Analyzers, 4Wire LCR Meters\\
& Multimeters, Root Cause Analysis, SMD Soldering, Prototyping \smallskip \\

Software Tools & JMP, Spice, AWR Microwave Office, CADSoft Eagle, IAR\\ 
 & Code Composer Studio, Eclipse, Git, SVN \smallskip \\

Programming Languages & Python, Matlab, C, LabView \smallskip \\ 

\end{tabular}

\end{rSection}
\smallskip

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}
\begin{rSubsection}{Apple Inc. -- Hardware Test Engineering}{October 2013 - Present}{Electrical Engineer}{Cupertino, CA}
\item Manage test vendors and contract manufacturers working on fast paced projects in order to provide test coverage for new product designs.
\item Work with cross functional engineering teams and vendors to expedite the root cause of test line issues.
\item Automate functional testing and data processing tasks using Python.
\item Design and implement test plans for component and system level testing on new product introductions of iOS devices and accessories.
\end{rSubsection}

%----------------------------------------------------------------------------------------

\begin{rSubsection2}{KLA-Tencor -- SensArray Group}{December 2011 - October 2013}{Electrical Engineer}{Milpitas, CA}

\pagebreak[2]
\begin{rWorkProject}{13.56MHz Displacement Current Calibration System}
\item Improved the existing resonant LC circuit in the calibration system by reducing the total DC resistance.
\item Built a higher quality factor LC circuit with a Q of 500 using a silver plated inductor and capacitor.
\item Designed and built a matching network to couple power into the higher Q LC system's inductor.
\item Designed and simulated a 13.56MHz Class E amplifier and matching network for use with the higher Q calibration system.
\end{rWorkProject}

\pagebreak[2]
\begin{rWorkProject}{RF Current Measurement Probe}
\item Worked on the design of an RF E-Field probe and detector circuit to measure field uniformity.
\item Developed firmware for an MSP430 to take differential measurements from the RF envelope detector circuit and store the results in flash memory on the MCU.
\item Worked with the senior electrical engineer, materials engineers, and packaging engineers to take the standalone design and integrate it into an existing measurement product for R\&D use at customer sites.
\end{rWorkProject}

\pagebreak[1]
\begin{rWorkProject}{Custom RFID System Improvements}
\item Characterized the existing 1MHz RFID communication system in order to identify areas for improvement.
\item Designed a band pass filter to select the 8kHz data from the output of the RFID coil envelope detector.
\item Built a proof of concept circuit with my band pass filter and a comparator to recover the digital data.
\item My design improved the bit error rate of the system by improving the selectivity of the detector.
\item Developed spice model of a newer thin film aluminum RFID antenna to predict the differences due to the distributed capacitance.
\end{rWorkProject}

\pagebreak[2]
\begin{rWorkProject}{Automated Curve Tracer Fault Detector}
\item Built a curve tracer using an Aglient U3606A power supply and multimeter combination and a 34970A mulitfunction meter.
\item Wrote a LabView application to sweep the compliance voltage, measure the current draw, and control the switch matrix cards.
\item The LabView application identified shorts between the silicon substrate and the network of thin film aluminum traces based on the peak current draw and the shape of the IV curve.
\end{rWorkProject}

\pagebreak[1]
\begin{rWorkProject}{High Density Plasma Chamber}
\item Maintained and updated legacy LabView control software handling the machine safety and system automation for the plasma chamber and supporting systems.
\item Diagnosed issues with the control systems, high vacuum systems, and robotic stages used on the plasma chamber.
\item Performed maintenance on the full system including the high voltage generator, RF generators, and matching networks.
\end{rWorkProject}

\pagebreak[1]
\begin{rWorkProject}{Embedded Temperature Measurement System RF Shielding}
\item Designed experiments to identify the primary interference mechanisms.
\item Built and tested experimental setups to measure the shielding efficacy from 1MHz up to 100MHz.
\item Worked with a team of Electrical Engineers, Physicists, and Materials Engineers to design shielding solutions that fit the existing system constraints.
\end{rWorkProject}

%\begin{rWorkProject}{}
%\end{rWorkProject}

\end{rSubsection2}

%----------------------------------------------------------------------------------------
\pagebreak[2]
\begin{rSubsection}{KLA-Tencor/SensArray Internship}{June 2005 - December 2011}{Electrical Engineering Intern}{Milpitas, CA}
\item Debugged and performed failure analysis on test systems, embedded hardware, and plasma systems.
\item Developed LabView applications to interface with test equipment and embedded systems for automated testing.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Personal & Student Projects SECTION
%----------------------------------------------------------------------------------------
\pagebreak[3]
\begin{rSection}{Personal \& Student Projects}

\begin{rProject}{Class D Amplifier - SJSU EE124 Final Project}{2012}
\item Designed a 10W class D amplifier using discrete components and operational amplifier ICs.
\item Built a 300kHz triangle wave generator in order to generate PWM from my audio with a comparator.
\item Built a power MOSFET output stage with gate driver and an LC low pass filter to drive the speaker.
\item Realized my entire design on a breadboard and demonstrated my amplifier as my final project in my analog design class.
\end{rProject}

\begin{rProject}{Bike Light - 1000 lm Headlamp and RGB Tail Lamp}{2012}
\item Designed a controller using an MSP430 MCU to manage the battery and control the LEDs.
\item Wrote firmware to schedule battery measurements, change LED duty cycles, and debounce a button for user input. 
\item Calculated power budget and selected appropriate LED drivers for my application.
\end{rProject}

\begin{rProject}{Formula Hybrid Vehicle Team - SJSU}{2010 - 2011}
\item Developed and tested battery management firmware for a dsPIC30 to perform pack safety monitoring and cell balancing.
\item Worked with teammates to debug their 10kW switching power converter stability and ringing issues.
\item Managed the EE team, developed project time lines, and drove schedules in order to meet our technical deadlines.
\item Presented team progress updates to the Silicon Valley IEEE Chapter Meeting as part of their continued funding of our student team.
\end{rProject}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\pagebreak[2]
\begin{rSection}{Education}

{\bf San Jose State University} \hfill {\em December 2011} \\ 
B.S. in Electrical Engineering \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
